### 2017-10-23 paper/sections/0_abstract.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale developers are abandoning POSIX IO because the file
system metadata synchronization and serialization overheads of providing strong
consistency and durability are too costly -- and often unnecessary -- for their
applications.  Unfortunately, designing file systems with weaker consistency or
durability excludes applications that rely on stronger guarantees, forcing
developers to re-write their applications or deploy them on a different system.
Mounting multiple systems in the global namespace forces users to (1) provision
separate storage clusters and (2) manually move data across systems.  We
present a framework and API that lets clients specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing users to optimize subtrees over time and space for
different workloads.  We confirm the performance benefits of techniques
presented in related work but also explore new consistency/durability metadata
designs, all integrated the same storage system.  By custom fitting a subtree
to a create-heavy application, we show 8\(\times\) speedup and 2\(\times\)
scale when compared to our baseline system.

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because the file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  Users can mount multiple systems in the
global namespace but this means (1) provisioning separate storage clusters and
(2) manually moving data across system boundaries.  We present a framework and
API that lets clients specify their consistency/durability requirements and
dynamically assign them to subtrees in the same namespace, allowing users to
optimize subtrees over time and space for different workloads.  We confirm the
performance benefits of techniques presented in related work but also explore
new consistency/durability metadata designs, all integrated over the same
storage system.  By custom fitting a subtree to a create-heavy application, we
show 8\(\times\) speedup and 2\(\times\) scale when compared to our baseline
system.

### 2017-10-23 paper/sections/1_introduction.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and data center applications  have
scalability problems because administrative tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current trends; for example, HPC architectures are transitioning from
complex storage stacks with burst buffer, file system, object store, and tape
tiers to more simplified stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put more pressure
on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

@@

Our prototype system, Cudele, achieves this by exposing ``mechanisms" that
developers use to specify their preferred semantics.  Cudele supports 3 forms
of consistency (invisible, weak, and strong) and 3 degrees of durability (none,
local, and global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. We make the following contributions:

@@

The last contribution lays the groundwork for future work on our prototype. It
is better than the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into CephFS for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. We
enable studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

% Results
The results in this paper lay the groundwork for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that the technique drastically improves performance (104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many clients
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We use Ceph as a prototyping platform because it
is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

>>>>

% What is the problem?
File system metadata services in HPC and data center applications  have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current hardware and software trends; for example, HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

@@

Our prototype system, Cudele, achieves this by exposing ``mechanisms" that
users combine to specify their preferred semantics.  Cudele supports 3 forms
of consistency (invisible, weak, and strong) and 3 degrees of durability (none,
local, and global) giving the user a wide range of policies and optimizations
that can be custom fit to an application. We make the following contributions:

@@

The last contribution lays the groundwork for future work on our prototype. It
is more scalable than the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into a Ceph file system (CephFS) for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. Our prototype
enables studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

% Results
The results in this paper pave the way for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that these techniques drastically improve performance (we see 104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many clients
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We use Ceph as a prototyping platform because it
is used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2017-10-23 paper/sections/3_posix_overheads.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many
creates, has the highest resource usage (combined CPU, network, and disk)
because of the number of RPCs needed for consistency and durability. The RPCs
are also serialized because the metadata server is single threaded; although
na\"{\i}ve, this design is common because of the complexity of multi-threaded
metadata servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  Traditional
file system techniques for improving performance, such as caching inodes, do
not help for create-heavy workloads.  In this section, we quantify the costs of
consistency and durability in CephFS.  At the end of each subsection we compare
the approach to ``decoupled namespaces", the technique in related work that
detaches subtrees from the global namespace to relax consistency/durability
guarantees.

@@

% what is durability
While durability is not specified by POSIX IO, users expect that files they
create or modify survive failures.  We define three types of durability:
global, local, and none.  Global durability means that the client or server can
fail at any time and metadata will not be lost because it is ``safe" ({\it
i.e.} striped or replicated across a cluster). Local durability means that
metadata can be lost if the client or server stays down after a failure. None
means that metadata is volatile and that the system provides no guarantees when
clients or servers fail.  None is different than local durability because
regardless of the type failure, metadata will be lost when components die in a
None configuration.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the
effect of journaling of different journal segment sizes; the larger the segment
size the bigger that the writes into the object store are. The trade-off for
better performance is memory consumption because larger segments take up
more space for buffering. When journaling is on, 
the metadata server periodically stops serving requests to flush ({\it i.e.}
apply journal updates) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store. We measured our peak bandwidth to
be 100MB/s, which is the speed of our network link.

\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS, to the
best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an
SSTable~\cite{ren:atc2013-tablefs}) then those batched metadata operations are
lost. For DeltaFS, if the client fails then, on restart, the computation does
the work again -- since the snapshots of the namespace are never globally
consistent and there is no ground truth.  On the server side, BatchFS and
DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which initially
reside in memory but are later flushed to the underlying distributed file
system.

@@

\textbf{CephFS Design}: Capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory (``interfere" curve
on \(y1\) axis) then the directory inode transitions out of read caching and
the first client must send \texttt{lookup()}s to the metadata server
(``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but performance suffers.  This degradation is shown in
Figure~\ref{fig:overhead-c}, where we scale the number of clients and show the
slowdown of the slowest client.  The results are normalized to a single
isolated client without a metadata server journal.  For the ``interfere" bars,
each client creates files in private directories and at 30 seconds we launch
another process that creates files in those directories. 18 clients is the
maximum number the metadata server could handle for this metadata-intensive
workload; at higher client load, the metadata server started complaining about
laggy and unresponsive requests.

@@

\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous to synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

>>>>

Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel in a CephFS mount.  The \texttt{untar} phase, which is
characterized by many creates, has the highest resource usage (combined CPU,
network, and disk) because of the number of RPCs needed for consistency and
durability. The RPCs are also serialized because the metadata server is single
threaded; although na\"{\i}ve, this design is common because of the complexity
of multi-threaded metadata
servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  In this section, we
quantify the costs of consistency and durability in CephFS.  At the end of each
subsection we compare the approach to ``decoupled namespaces", the technique in
related work that detaches subtrees from the global namespace to relax
consistency/durability guarantees.

@@

% what is durability
While durability is not specified by POSIX IO, users expect that files they
create or modify survive failures.  We define three types of durability:
global, local, and none.  Global durability means that the client or server can
fail at any time and metadata will not be lost because it is ``safe" ({\it
i.e.} striped or replicated across a cluster). Local durability means that
metadata can be lost if the client or server stays down after a failure. None
means that metadata is volatile and that the system provides no guarantees when
clients or servers fail.  None is different than local durability because
regardless of the type of failure, metadata will be lost when components die in a
None configuration.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling of with different
segment sizes; the larger the segment size the bigger that the writes into the
object store are. The trade-off for better performance is memory consumption
because larger segments take up more space for buffering. When journaling is
on, the metadata server periodically stops serving requests to flush ({\it
i.e.} apply journal updates) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store.

\textbf{Comparison to decoupled namespaces}: For BatchFS, if a client fails
when it is writing to the local log-structured merge tree (implemented as an
SSTable~\cite{ren:atc2013-tablefs}) then unwritten metadata operations are
lost. For DeltaFS, if the client fails then, on restart, the computation does
the work again -- since the snapshots of the namespace are never globally
consistent and there is no ground truth.  On the server side, BatchFS and
DeltaFS use IndexFS~\cite{ren:sc2014-indexfs}. IndexFS writes metadata to
SSTables, which initially reside in memory but are later flushed to the
underlying distributed file system.

@@

\textbf{CephFS Design}: Capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading and writing inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:overhead-b}. The colors show the behavior of the client for two
different runs.  If only one client is creating files in a directory
(``isolated" curve on \(y1\) axis) then that client can lookup the existence of
new files locally before issuing a create request to the metadata server. If
another client starts creating files in the same directory then the directory
inode transitions out of read caching and the first client must send
\texttt{lookup()}s to the metadata server (``interfere" curve on \(y2\) axis).
These extra requests increase the throughput of the ``interfere" curve on the
\(y1\) axis because the metadata server can handle the extra load but
performance suffers.  This degradation is shown in Figure~\ref{fig:overhead-c},
where we scale the number of clients and show the slowdown of the slowest
client.  The results are normalized to a single isolated client without a
metadata server journal and the error bars are the standard deviations of all
client runtimes.  For the ``interfere" bars, each client creates files in
private directories and at 30 seconds we launch another process that creates
files in those directories. 18 is the maximum number of clients the metadata
server can handle for this metadata-intensive workload; at higher client load,
the metadata server complains about laggy and unresponsive requests.

@@

\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous and synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

### 2017-10-23 paper/sections/4_methodology.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this section we describe Cudele, our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct \textbf{policies}.
These policies are assigned to subtrees and they dictate how the file system
should handle operations within that subtree.  Below, we describe the
mechanisms (which are \underline{underlined}), the policies, and the API for assigning
policies to subtrees.

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by.  Table~\ref{table:mechanisms} has a
description of what each mechanism does.  Decoupled clients use the
\underline{Append Client Journal} mechanism to append metadata updates to a
local, in-memory journal. This is fast because clients do not need to check for
consistency when writing events and the metadata server blindly applies the
updates because it assumes the events were already checked for consistency. The
trade-off here is performance; it is a dangerous approach but could be
implemented safely if the clients or metadata server are configured to check
the validity of events before writing them.  Once the job is complete, the
system calls Cudele mechanisms to achieve the desired consistency/durability
semantics.  Cudele provides a library for clients to link into and all
operations are performed by the client.

\subsubsection{Mechanisms Used for Consistency} \underline{RPCs} send remote procedure
calls for every metadata operation from the client to the metadata server,
assuming the request cannot be satisfied by the inode cache. This mechanism is
part of the default CephFS implementation and is the strongest form of
consistency because clients see metadata updates right away.  \underline{Nonvolatile
Apply} replays the client's journal onto the metadata cluster's metadata store.
The client's in-memory journal is written into the object store and the
metadata servers are restarted. When the metadata servers re-initialize, they
notice new journal updates in the object store and replay the events onto their
in-memory metadata stores.  \underline{Volatile Apply} takes the client's in-memory journal on the
client and applies the updates directly to the in-memory metadata store maintained
by the metadata servers. We say volatile because -- in exchange for peak
performance -- Cudele makes no consistency or durability guarantees while
Volatile Apply is executing.  If a concurrent update from a client occurs
there is no rule for resolving conflicts and if the client or metadata server
crashes there may be no way to recover.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings in
Ceph we can turn Stream on and off.  If it is off, then the metadata servers
will not save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global Persist},
clients push the journal into the objects store. The overheads for both Local
Persist and Global Persist is the write bandwidth of the local disk and
object store, respectively.  These persist mechanisms are part of the library that
links into the client.

@@

  \item \texttt{interfere\_policy}: how to handle a request from another
  client targeted at this subtree (\texttt{allow}))

@@

The ``Consistency" and ``Durability" parameters are set to the Cudele
mechanisms; they can be composed (\(+\)) or run in parallel (\(|\|\)).
``Allocated Inodes" is a way for the application to specify how many files it
intends to create. It is a contract so that the file system can provision
enough resources for the incumbent merge and so it can give valid inodes to
other clients. The inodes can be used anywhere within the decoupled namespace
({i.e.} at any depth in the subtree).

% description
``Interfere Policy" has two settings: \texttt{block} and \texttt{allow}.
For \texttt{block}, any requests to this part of the namespace returns with
``Device is busy", which will spare the metadata server from wasting resources
for updates that may get overwritten. If the application does not mind losing
updates, for example it wants approximations for results that take too long to
compute, it can select \texttt{allow}. In this case, metadata from the interfering client will be
written and the computation from the decoupled namespace will take priority at
merge time because the results are more accurate.

% examples
Given these default values decoupling the namespace with an empty policies file
would give the application 100 inodes but the subtree would behave like the
existing CephFS implementation.  BatchFS merges updates into the global
namespace after the job is complete.  This can be achieved with by composing
two mechanisms:

>>>>

In this section we describe our API and framework that lets users
assign consistency and durability semantics to subtrees in the global
namespace. A \textbf{mechanism} is an abstraction and basic building block for
constructing consistency and durability guarantees. Cudele exposes these
mechanisms and the user composes them together to construct \textbf{policies}.
These policies are assigned to subtrees and they dictate how the file system
should handle operations within that subtree.  Below, we describe the
mechanisms (which are \underline{underlined}), the policies, and the API for assigning
policies to subtrees.

@@

% describe the figure
Figure~\ref{fig:decouple} shows the mechanisms (labeled arrows) in Cudele and
which daemon(s) they are performed by.  Table~\ref{table:mechanisms} has a
description of what each mechanism does.  Decoupled clients use the
\underline{Append Client Journal} mechanism to append metadata updates to a
local, in-memory journal. Clients do not need to check for
consistency when writing events and the metadata server blindly applies the
updates because it assumes the events were already checked for consistency. The
trade-off here is fast performance; it is a dangerous approach but could be
implemented safely if the clients or metadata server are configured to check
the validity of events before writing them.  Once the job is complete, the
system calls mechanisms to achieve the desired consistency/durability
semantics.  Cudele provides a library for clients to link into and all
operations are performed by the client.

\subsubsection{Mechanisms Used for Consistency} \underline{RPCs} send remote
procedure calls for every metadata operation from the client to the metadata
server, assuming the request cannot be satisfied by the inode cache. This
mechanism is part of the default CephFS implementation and is the strongest
form of consistency because clients see metadata updates right away.
\underline{Nonvolatile Apply} replays the client's in-memory journal into the
object store and restarts the metadata servers. When the metadata servers
re-initialize, they notice new journal updates in the object store and replay
the events onto their in-memory metadata stores.  \underline{Volatile Apply}
takes the client's in-memory journal on the client and applies the updates
directly to the in-memory metadata store maintained by the metadata servers. We
say volatile because -- in exchange for peak performance -- Cudele makes no
consistency or durability guarantees while Volatile Apply is executing.  If a
concurrent update from a client occurs there is no rule for resolving conflicts
and if the client or metadata server crashes there may be no way to recover.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings in
Ceph we can turn Stream on and off.  If it is off, then the metadata servers
will not save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global Persist},
clients push the journal into the object store. The overheads for both Local
Persist and Global Persist is the write bandwidth of the local disk and
object store, respectively.  These persist mechanisms are part of the library that
links into the client.

@@

  \item \texttt{interfere\_policy}: how to handle a request from another
  client targeted at this subtree (\texttt{allow})

@@

The ``Consistency" and ``Durability" parameters are compositions of mechanisms;
they can be serialized (\(+\)) or run in parallel (\(|\|\)).  ``Allocated
Inodes" is a way for the application to specify how many files it intends to
create. It is a contract so that the file system can provision enough resources
for the incumbent merge and so it can give valid inodes to other clients. The
inodes can be used anywhere within the decoupled namespace ({i.e.} at any depth
in the subtree).  ``Interfere Policy" has two settings: \texttt{block} and
\texttt{allow}.  For \texttt{block}, any requests to this part of the namespace
returns with ``Device is busy", which will spare the metadata server from
wasting resources for updates that may get overwritten. If the application does
not mind losing updates, for example it wants approximations for results that
take too long to compute, it can select \texttt{allow}. In this case, metadata
from the interfering client will be written and the computation from the
decoupled namespace will take priority at merge time because the results are
more accurate.  Given these default values decoupling the namespace with an
empty policies file would give the application 100 inodes but the subtree would
behave like the existing CephFS implementation.

### 2017-10-23 paper/sections/5_implementation.tex
paper: final read-through
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% how i used it
\textbf{Cudele}: the ``RPCs" mechanism uses the metadata store to
service requests. Using code designed for recovery, ``Nonvolatile Apply" and
``Volatile Apply" replay updates onto the metadata store in memory and in the
object store, respectively.  When the clients are ready to merge their updates
back into the global namespace, they pass a binary file of  metadata updates to
the metadata server.

@@

\textbf{Cudele}: the journal format is used by ``Stream", ``Append Client Journal",
``Local Persist", and ``Global Persist".  ``Stream" is the default
implementation for achieving global durability in CephFS but the rest of the
mechanisms are implemented by writing with the journal format.  By writing with
the same format, the metadata servers can read and use the recovery code to
materialize the updates from a client's decoupled namespace ({\it i.e.} merge).
These implementations required no changes to CephFS because the metadata
servers know how to read the events the library is writing.  By re-using the
journal subsystem to implement the namespace decoupling, Cudele leverages the
write/read optimized data structures, the formats for persisting events
(similar to TableFS's SSTables~\cite{ren:atc2013-tablefs}), and the functions
for replaying events onto the internal namespace data structures.

@@

\textbf{Cudele}: the external library the clients link into is based
on the journal tool. It already had functions for importing, exporting, and
modifying the updates in the journal so we re-purposed that code to implement
``Append Client Journal", ``Volatile Apply", and ``Nonvolatile Apply".

@@

\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.

>>>>

% how i used it
\textbf{Cudele}: the RPCs mechanism uses the metadata store to
service requests. Using code designed for recovery, Nonvolatile Apply and
Volatile Apply replay updates onto the metadata store in memory and in the
object store, respectively.  When the clients are ready to merge their updates
back into the global namespace, they pass a binary file of  metadata updates to
the metadata server.

@@

\textbf{Cudele}: the journal format is used by Stream, Append Client Journal,
Local Persist, and Global Persist.  Stream is the default
implementation for achieving global durability in CephFS but the rest of the
mechanisms are implemented by writing with the journal format.  By writing with
the same format, the metadata servers can read and use the recovery code to
materialize the updates from a client's decoupled namespace ({\it i.e.} merge).
These implementations required no changes to CephFS because the metadata
servers know how to read the events the library is writing.  By re-using the
journal subsystem to implement the namespace decoupling, Cudele leverages the
write/read optimized data structures, the formats for persisting events
(similar to TableFS's SSTables~\cite{ren:atc2013-tablefs}), and the functions
for replaying events onto the internal namespace data structures.

@@

\textbf{Cudele}: the external library the clients link into is based
on the journal tool. It already had functions for importing, exporting, and
modifying the updates in the journal so we re-purposed that code to implement
Append Client Journal, Volatile Apply, and Nonvolatile Apply.

@@

\textbf{Cudele}: Nonvolatile Apply uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.
